Innovations Report: Procedural Fur System

### 2018-03-16 docs/paper.tex
more on docs

The most popular of these is XGen, originally developed by Walt Disney Animation Studios, which has been included in Autodesk's Maya since 2014. XGen uses a 'Collection' and 'Description' paradigm; Descriptions store user controlled parameters which affect fur primitives (curves for example) on a select area of a mesh, and Collections act as a container for these Descriptions. There are two primary methods offered for distributing primitives on a mesh, Guide Curves can be used to manually control the placement and shape of primitives by placing 'Guides' on the mesh surface, whereas 'Groomable Splines' randomly distirbutes splines over the mesh surface which can be manipulated in real time using viewport manipulators that mimic the brushing and styling of fur. In both modes, 'modifiers' can be added to the modifier stack to further adjust the visual outcome, adding features such as clumping, noise, and coiling. Attributes within these modifiers can be further controlled using expressions or texture maps.

@@

Offerering even even more flexibility, recent versions of SideFX's Houdini include hair and fur operator nodes, which create predefined node networks for the generation of hair and fur. These networks use standard Houdini nodes internally, so experienced Houdini users are intuitively able to create the visual outcome they desire, using tools they already know. However, it may be quite unintuitive for asset artists (those who would be using the tool, Groom artists?), who are not used to Houdini's heavily procedural workflow.

@@

\begin{itemize}
	\item Geometry Loaders - These are responsible for loading user specified geometry. Example Geometry Loaders could allow for the parsing of Wavefront OBJ files.
	\item Distributors - These are responsible for the distribution of curves onto user specified geometry. User controllable parameters could include density (curve count), distribution pattern (random, uniform), and curve length. These parameters could potentially be controlled by texture inputs.
	\item Operators - These are responsible for manipulation of the curves to achieve the desired look. Example operators could provide bending, clumping, or randomisation of input curves.
	\item Renderers - These are responsible for the rendering of curves into the application viewport. Example renderers could provide mesh, cuves as lines, or curves as ribbons rendering functionality. User controllable parameters could provide controls for the shading model in use, as well as control of the base and tip widths when rendering curve ribbons for example.
\end{itemize}

@@

@@

\section{Results} \label{sec:results}
Results Text.

@@

\begin{figure}[htbp]\centering
\begin{center}
\begin{tabular}{||c|c||}
\hline
Mesh Triangle Count & GPU Time (ms)\\
\hline
\hline
16 (Triangle Strip) & 18 - 20\\
\hline
4968 (Stanford Bunny) & 33 - 45\\
\hline
14067 (Utah Teapot) & 76 - 92\\
\hline
\end{tabular}
\caption{\label{figure:fullPerformance} Performance metrics showing the time taken to perform a full graph evaluation on a complex setup, as seen in INSERT PIC, for meshes of varying triangle counts.}
\end{center}
\end{figure}

>>>>

The most popular of these is XGen, originally developed by Walt Disney Animation Studios \cite{xgen}, which has been included in Autodesk's Maya since 2014. XGen uses a 'Collection' and 'Description' paradigm; Descriptions store user controlled parameters which affect fur primitives (curves for example) on a select area of a mesh, and Collections act as a container for these Descriptions. There are two primary methods offered for distributing primitives on a mesh, Guide Curves can be used to manually control the placement and shape of primitives by placing 'Guides' on the mesh surface, whereas 'Groomable Splines' randomly distirbutes splines over the mesh surface which can be manipulated in real time using viewport manipulators that mimic the brushing and styling of fur. In both modes, 'modifiers' can be added to the modifier stack to further adjust the visual outcome, adding features such as clumping, noise, and coiling. Attributes within these modifiers can be further controlled using expressions or texture maps.

@@

Offerering even more flexibility, recent versions of SideFX's Houdini include hair and fur operator nodes, which create predefined node networks for the generation of hair and fur. These networks use standard Houdini nodes internally, so experienced Houdini users are intuitively able to create the visual outcome they desire, using tools they already know. However, it may be quite unintuitive for asset artists (those who would be using the tool, Groom artists?), who are not used to Houdini's heavily procedural workflow.

@@

\begin{itemize}
	\item Geometry Loaders - These are responsible for loading user specified geometry. Example Geometry Loaders could allow for the parsing of Wavefront OBJ files.
	\item Distributors - These are responsible for the distribution of curves onto user specified geometry. User controllable parameters could include density (curve count), distribution pattern (random, uniform), and curve length. These parameters could potentially be controlled by texture inputs.
	\item Operators - These are responsible for manipulation of the curves to achieve the desired look. Example operators could provide bending, clumping, or randomisation of input curves. These should behave much like the 'Modifiers' in XGen.
	\item Renderers - These are responsible for the rendering of curves into the application viewport. Example renderers could provide mesh, cuves as lines, or curves as ribbons rendering functionality. User controllable parameters could provide controls for the shading model in use, as well as control of the base and tip widths when rendering curve ribbons for example.
\end{itemize}

@@

Once curve primitives have been generated, they need to be passed onto curve operators, which perform most of the work towards creating an appealing visual output. I decided to create an abstract curve operator node, much like I had with the distributor node, which contains a virtual function for performing the curve manipulation.

@@

\section{Results} \label{sec:results}

\begin{figure}[htbp]\centering
\includegraphics[width=1.0\linewidth]{images/test_0007}
\caption{\label{figure:screenshot} An example of the visual output that the system is capable of producing.}
\end{figure}

Results Text.

@@

\begin{figure}[htbp]\centering
\begin{center}
\begin{tabular}{||c|c||}
\hline
Mesh Triangle Count & GPU Time (ms)\\
\hline
\hline
16 (Triangle Strip) & 18 - 20\\
\hline
4968 (Stanford Bunny) & 33 - 45\\
\hline
14067 (Utah Teapot) & 76 - 92\\
\hline
\end{tabular}
\caption{\label{figure:fullPerformance} Performance metrics showing the time taken to perform a full graph evaluation on a complex setup, as seen in Figure~\ref{figure:screenshot}, for meshes of varying triangle counts.}
\end{center}
\end{figure}
